\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\it \hfill\today}%
% \let\@evenfoot\@oddfoot}
%\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Additional brackets around year in citations},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)
% Pandoc header


\usepackage[nomarkers]{endfloat}

\begin{document}
\begin{frontmatter}

  \title{Additional brackets around year in citations}
    \author[WUT]{Mateusz Kędzior\corref{c1}}
   \ead{alice@sample.com} 
   \cortext[c1]{Corresponding Author}
    
  \begin{abstract}
  First line
  
  The second line
  \end{abstract}
   \begin{keyword} some \sep thing \sep some \sep where \sep \end{keyword}
 \end{frontmatter}

\section{What I receive}\label{what-i-receive}

Cite only one article: Shelah
(\protect\hyperlink{ref-Sh:2}{1969}\protect\hyperlink{ref-Sh:2}{a})

It was mentioned in: Shelah
(\protect\hyperlink{ref-Sh:1}{1969}\protect\hyperlink{ref-Sh:1}{b});
Shelah
(\protect\hyperlink{ref-Sh:2}{1969}\protect\hyperlink{ref-Sh:2}{a});
Shelah (\protect\hyperlink{ref-Sh:3}{1970})

It was mentioned in (Shelah, \protect\hyperlink{ref-Sh:3}{1970},
\protect\hyperlink{ref-Sh:1}{1969}\protect\hyperlink{ref-Sh:1}{b},
\protect\hyperlink{ref-Sh:2}{1969}\protect\hyperlink{ref-Sh:2}{a})

\section{Expected result}\label{expected-result}

I wish to have something like:

It was mentioned in (Shelah, 1969b; Shelah, 1969a; Shelah, 1970)

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Sh:3}{}
Shelah, S., 1970. Finite diagrams stable in power. Annals of
Mathematical Logic 2, 69--118.

\hypertarget{ref-Sh:2}{}
Shelah, S., 1969a. Note on a min-max problem of Leo Moser. Journal of
Combinatorial Theory 6, 298--300.

\hypertarget{ref-Sh:1}{}
Shelah, S., 1969b. Stable theories. Israel Journal of Mathematics 7,
187--202.

\end{document}


